\chapter{Introduction}

%https://www.myperfectwords.com/blog/thesis-writing/writing-a-thesis-introduction

% Attention grabbing hook statement
Railway operation is undergoing rapid changes.
%
% General introduction to topic through general statements
As digitalization progresses, a trend towards the \abr{IOT} is developing and devices such as vehicles and machines become interconnected~\cite{RailwayDigitalization}.
With the increasing traffic and the importance of the railway in the transportation of persons and goods alike, digitization offers a way to deal with growing complexity.

On the one hand, improvements in computation and communication technologies, as well as in railway applications, laid the foundation for building safe and reliable systems.
Studies have shown that 41\% of all railway accidents were caused by human failures~\cite{StudyRailwayAccidents}.
At the same time, \abr{SIL} 4 certified \abr{ATO} systems with a small \abr{PFD}~\cite{SallekSIL} are possible.
Further, the standardization of signaling and control components in the \abr{ETCS} facilitated train operation across borders and increased the significance of \abr{ATO} systems~\cite{YIN2017RNDofATO}.

On the other hand, the automation of railway operations comes with higher development and acquisition costs, as well as ethical issues.
System designers must specify the system's reaction under specific conditions and balance the safety of humans, such as passengers and road users, and of resources, such as costs and time~\cite{EthicsInSafety}.

Hence, with the railway being a safety-critical system, any component applied in the \abr{ETCS} context must comply with strict certification requirements to assure its safety and reliability.
Compliance with system requirements is ensured during an approval process.
The thereby applied verification, validation, and certification steps are time- and cost-intensive, which adds to the already high development costs.
Moreover, the approval process needs to be repeated every time the system gets updated.
Increasing costs for \abr{ETCS} systems could lead to a situation where it is not profitable to equip certain regions, connections, or train models with \abr{ETCS}.
\\

Distributed computation is a way to reduce the costs of repeated approval processes and increase scalability.
Therefore, autonomous computing elements - that each performs a subset of the system's requirements - are interconnected~\cite{DistributedSafety2020}.
However, distributed systems also introduce new challenges such as coping with the communication overhead and dealing with node-, network-, and computation faults.

A fundamental technique for coping with faults in a computing system is redundancy~\cite{TanenbaumSteen07}.
In redundant computation, safety-critical calculations are performed in parallel in a distributed manner and combined afterwards.
Generally speaking, redundancy entails additional resources that are not required for a system's functional operation but add specific characteristics such as fault detection and fault tolerance~\cite{BarryFaultToleranceAnalysis}.
Various well-established redundancy patterns have been proven in practice, including hardware-, software-, information-, and time redundancy.
In contrast to non-redundant systems, redundancy allows building safe systems out of less safe and cheaper parts.
\\

For handling communication in distributed systems, different concepts, standards, and frameworks exist.
One of them is \abr{DDS}, a \abr{DCPS} standard for machine-to-machine communication that is specified by the \abr{OMG}~\cite{omgDDSspec}.
\abr{DDS} is designed for facilitating safe and real-time communication among distributed and autonomous execution units and is therefore applicable for building safety-critical systems~\cite{DistributedSafety2020}.
The standard, which is intended to be implemented as a middleware, allows the specification of \abr{QOS} to define the service's behavior in a declarative way.
Through the \abrpl{QOS}, the communication can be defined to be reliable and real-time.

However, \abr{DDS} has been designed to be a generic standard for distributed application communication and integration and therefore provides a wide variety of features~\cite{omgDDSspec}.
Hence, every feature from the applied middleware implementation needs to be approved when applied in a safety-critical application.
\\

In this thesis, it is investigated whether the \abr{DDS} standard is applicable for building redundant, distributed, real-time, and safety-critical systems in the \abr{ETCS} domain.
One of the main requirements is that the application should run on general-purpose \abrpl{PLC} with limited resources without violating safety and reliability requirements.
This work makes the following \textit{contributions}:

\begin{enumerate}
\item An analysis and comparison of different established redundancy concepts based on their reliability and implementability with \abr{DDS}.
\item Elaboration and implementation of a consensus-based redundant architecture based on a fault model of an \abr{ETCS} subset.
\item A proof-of-concept evaluation of the implementation towards functionality, safety, and implementability with \abr{DDS}.
\item A sufficient \abr{DDS} subset for building a safety-critical and real-time distributed system.
\end{enumerate}

\paragraph{Structure}
First, an overview of popular redundancy patterns and characteristics for building safe and reliable systems, as well as about \abr{ETCS} and \abr{DDS}, is given in~\autoref{chptr:concepts}.
Afterward, mathematical concepts for evaluating the safety and reliability of these systems are pointed out.
A selection of related work that uses \gls{DDS} in safety-critical applications is presented and set in relation to this work at the end of chapter 2.
\\

In~\autoref{chptr:redundantSystemsCompare}, key building blocks for designing distributed systems with the \abr{DDS} standard are described.
The redundancy concepts and patterns previously presented are opposed and evaluated based on the characteristics from chapter 2.
Further, each pattern's exemplary concepts and architectures are described and assessed based on their safety and realizability with \abr{DDS} concepts.
Therefore, not only voting-based concepts but also a way of building consensus-driven redundant systems are described and analyzed.
A combination of a consensus- and voting-based approach is identified as the most suitable concept for satisfying the desired system's requirements.
\\

In~\autoref{cpt:Implementation}, an exemplary implementation is presented that follows the concepts of \texttt{Raft}~\cite{RaftConsensusPaper}.
Thereby, the significance of a safe consensus- and voting-based redundant system, which utilizes \abr{DDS} for communication, is shown.
The system comprises of four homogeneous and interconnected \textit{Revolution Pi} from Kunbus~\cite{Kunbus} and utilizes \textit{OpenSplice DDS} from ADLINK~\cite{VortexOpenSplice} as a \abr{DDS} framework.
A \textit{Revolution Pi} is a robust \abr{PLC} that build upon a \textit{Raspberry Pi} and features a real-time capable \abr{OS}.
The \textit{OpenSplice DDS} framework's applicability for safety-critical railway applications has been proven in practice~\cite{SchmidtMissionCriticalChallenges}.
\\

Afterward, the implemented system's safety and functional correctness are proven based on a simulated \abr{ETCS} scenario in~\autoref{cpt:evaluation}.
In addition, the system's time performances and hardware resource utilization is examined.
Results show the system runs the simulated scenarios successfully and all requirements are met, even when an entire component fails.
Finally, the applied \abr{DDS} subset is listed and justified.


%TODO Mention results and main realization

